Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.}
\label{fig:filtered-signal}
\end{figure}

@@

We report here experiments on the \textit{normal-1,2,3}, and \textit{4}
datasets provided by the organizers of the Connectomics challenge (see
Appendix~\ref{app:supp} for experiments on other datasets). Each of
these datasets is obtained from the simulation \citep{stetter2012model} of
different neural networks of 1000 neurons and about 15000 edges each (i.e., a
network density of about 1.5\%). Each neuron is described by a calcium
fluorescence time series of length $T=179500$. All inference methods compared
here provide a ranking of all pairs of neurons according to some association
score. To assess the quality of this ranking, we compute both ROC and
precision-recall curves against the ground truth network, which are summarized
using the area under the curve and respectively  denoted AUROC and AUPRC. Only
the AUROC score was used to rank the challenge participants but the precision-
recall curve has been shown to be a more sensible metric for network
inference, especially when network density is small (see e.g.,
\cite{schrynemackers2013protocols}). Since neurons are not self-connected in
the ground truth networks (i.e., $(i, i) \not \in E, \forall i \in V$), we
have manually set the score of such edges to the minimal possible association
score before computing ROC and PR curves.

>>>>

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
\caption{Signal processing pipeline for extracting peaks from the raw fluorescence data.}
\label{fig:filtered-signal}
\end{figure}

@@

We report here experiments on the \textit{normal-1,2,3}, and \textit{4}
datasets provided by the organizers of the Connectomics challenge (see
Appendix~\ref{app:supp} for experiments on other datasets). Each of
these datasets is obtained from the simulation \citep{stetter2012model} of
different neural networks of 1000 neurons and about 15000 edges each (i.e., a
network density of about 1.5\%). Each neuron is described by a calcium
fluorescence time series of length $T=179500$. All inference methods compared
here provide a ranking of all pairs of neurons according to some association
ssociation
score. To assess the quality of this ranking, we compute both ROC and
precision-recall curves against the ground truth network, which are summarized
using the area under the curve and respectively  denoted AUROC and AUPRC. Only
the AUROC score was used to rank the challenge participants but the precision-
recall curve has been shown to be a more sensible metric for network
inference, especially when network density is small (see e.g.,
\cite{schrynemackers2013protocols}). Since neurons are not self-connected in
the ground truth networks (i.e., $(i, i) \not \in E, \forall i \in V$), we
have manually set the score of such edges to the minimal possible association
score before computing ROC and PR curves.
